---
output:
  md_document:
    variant: markdown_github
---



```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# The 'datzen' R Package of Miscellaneous Helper Functions the Zen Way

The **datzen** package provides three categories of commonly used Zen functions:

* data in / out  
* themes (rebranded functions and visual aesthetics)  
* special computation functions  

The goal of this package is to help data analysts rapidly prototype common analysis scripts.

```{r message=FALSE}
# devtools::install_github('mikejacktzen/datzen',force=TRUE)  
library(datzen)
library(dplyr)
```

## Data I/O

### Ever wanted a generic simulated dataset to prototype modeling commands?

How did you know? I hate using `data(iris)` because the column names aren't generic enough!

```{r}
simlm(p=7,n=5,output_meta=TRUE)

simlm(p=3,n=100,coef_true = c(69,23,7),output_meta=TRUE)$yx %>% lm(data=., y ~ -1+.)
```


### Ever wanted to read in 5 random rows of some physical spreadsheet?

Someone handed me this dumb csv with 100 columns. I don't even know what's in it!

```{r message=FALSE}

set.seed(1); m = matrix(rnorm(100*100),ncol=100,nrow=100)
csv = data.frame(m)
dim(csv)

tf <- tempfile()
write.csv(csv,tf,row.names=FALSE)
```

So... of course! I want to use lightweight data and quickly piece together code before I run it on the full data!

```{r message=FALSE}
freadss(input=tf,ss=5,replace=TRUE) %>% dim
```


## Themes

### I forgot about the wierd base R name of that link function used in logistic regression.

Uhhh, it was what's his face! The one with the logis!

Oh, you mean logit?

```{r}
# ?logit
identical(logit(0.5),stats::qlogis(0.5))
txtplot::txtplot(x=seq(from=0.01,to=0.99,by=0.01),y=logit(seq(from=0.01,to=0.99,by=0.01)))

```

I forgot about the wierd name of its inverse function too!
Oh yeah... his ugly cousin, plogis.
I know him as expit.

```{r}
# ?expit
identical(expit(10),stats::plogis(10))
txtplot::txtplot(x=seq(from=-10,to=10,by=1),y=expit(seq(from=-10,to=10,by=1)))

```

### Ever wanted a random string of garbage?

I'm too much of a homo-sapien, my phrases are never random enough?! 
I wish I could be more like a homo-erectus, or a computer.

```{r}
thats_what_she_said = 10

garble(size_out=thats_what_she_said)

junk = garble(size_out=thats_what_she_said)

```

### Is your workspace environment too clutered? 

It was like that when I got here.

```{r}
jimmy = 'johns'
nuts = 'planters'

ls()
```

I want to remove **All But Deeze** ...

```{r}
rmabd('nuts')

ls()
```


